\section*{Acknowledgements}

I have had the great fortune of working alongside many incredibly talented people
during my time in the Robotics Institute, all of whom contributed in some part to
this thesis and to my future. I am thankful to those who have given me support
and encouragement through what most consider to be a selfish endeavor.

I would first like to thank Prof. Nathan Michael, my advisor, for his immense
help in shaping my research interests, providing critical writing and
presentation feedback, and for the significant one-on-one time that he put into teaching me
the art and science of robotics.

The members of the Robust Adaptive Systems Lab (RASL) have been an invaluable
resource for solving difficult problems, and for providing hope and comfort
during stressful times. I am thankful to Vishnu Desaraju, John Yao,
Derek Mitchell, and Shihyun Lo for putting everything into perspective, and for
guidance through tricky problems in planning, state estimation, and control
theory.

My experiences at Carnegie Mellon University would not have been nearly as
enjoyable or productive without the friends that I made along the way. Thank you
Nick Gisolfi, Zach Batts, and Allie Del Giorno for balancing my life with music,
philosophy, politics, and even more robotics.

Finally, I would like to thank the people in my life that guided me into doing
what I now love. Thanks to Profs. Zo\"{e} Wood, Jane Lehr, and Chris Clark, who
encouraged and persuaded me to attend graduate school in the first place.
Thanks to Alex Viksne, my parents, and my sister, who supported me unconditionally.
